Collective behavior of Janus Particles Suspended in a Viscous Fluid

### 2022-07-20 doc/PRF2022/PRF_main.tex
yny 0720 6

In case (ii) with $b = 1$, the boundary condition is everywhere positive.
It takes the maximum value $3a$ on tail (red) and the
minimum value $a$ on the head side (yellow). 
Both sides of the Janus particle are hydrophobic but
moreso on the $\alpha = 0$ side.  
Over a short time scale, these particles also self-assemble into bilayers. But unlike for case (i),
the heads are also hydrophobic and so in the long-time dynamics
these bilayers form multilamella structures.
The number of folds depends primarily on the number of particles.
Figure~\ref{fig:relax}(c), for example, shows a
multilamellar structure with four layers and one with two layers in the inset.

A water structure with
positive/negative charge is possible in case (iii), $b = 0$
\cite{MaRa76, Ma77}.
Here, the head repels the tail of other particles
and the particles initially form chains with their directors perpendicular
to the length of the chain.  
The chains form stria
where the particles lie on a 
square grid and the orientations alternate
between layers (Figure~\ref{fig:relax}(d)).

>>>>

In case (ii) with $b = 1$, the boundary condition is everywhere positive.
It takes the maximum value $3a$ on tail (red) and the
minimum value $a$ on the head side (yellow). 
Both sides of the Janus particle are hydrophobic but
more so on the $\alpha = 0$ side.  
Over a short time scale, these particles also self-assemble into bilayers. But unlike for case (i),
the heads are also hydrophobic and so in the long-time dynamics
these bilayers form multilamella structures.
The number of folds depends primarily on the number of particles.
Figure~\ref{fig:relax}(c), for example, shows a
multilamellar structure with four layers and one with two layers in the inset.

In case (iii) with $b=1$,
a water structure with
positive/negative charge is possible \cite{MaRa76, Ma77}.
Here, the head repels the tail of other particles
and the particles initially form chains with their directors perpendicular
to the length of the chain.  
The chains form stria
where the particles lie on a 
square grid and the orientations alternate
between layers (Figure~\ref{fig:relax}(d)).
